---
title: "Rmarkdown for Lab2 of Bio4315"
author: "David Shmil"
date: "2024-09-19"
output: html_document
---

# This is a r markdown for lab 2

---
Code chunk loading vegan and ggplot2
---
```{r, warning=FALSE, message=FALSE}
library(vegan)
library(ggplot2)


```

---
Code chunk loading dune data and then performing log on the data
---
```{r}
data(dune)
dune2<-dune
log_of_dune<-log1p(dune2)

```

---
Code chunk performing metaMDS on dune2 and then assigning the points to a variable called dpoints
---
```{r}
metaMDS_dune<-metaMDS(dune2)
dpoints<-metaMDS_dune$points

```

---
Code chunk transforms dpoints into a dataframe and then uses ggplot to make a scatter plot using the MDS1 and MDS2 columns from dpoints with a black and white theme. Afterwards it saves the data as a pdf
---
```{r}
data_frame_of_dpoints<-data.frame(dpoints)

ggplot(data_frame_of_dpoints, aes(x= MDS1,y= MDS2))+geom_point()+theme_bw()+ggtitle(label="Scatter Plot of MDS1 vs MDS2")
ggsave(filename = "Scatter Plot Lab 2.pdf")

```